6.1:
Compute a Monte Carlo estimate of
integrate(sin(t)dt, l=0, u=pi/3)

and compare your estimate with the exact value of the integral

```{r}
f = function(x) {
  return (sin(x))
}

I = integrate(f, lower=0, upper=pi/3)

I$value
```

```{r}
m = 100000
a = 0
b = pi/3

X = runif(m, a, b)

gx_hat = mean(f(X))

theta_hat = (b - a) * gx_hat

theta_hat

```

theta_hat = 0.5011098
exact_value = 0.5

--------------------------------------------------------------------------------
6.3
Compute a Monte Carlo estimate ˆθ of
theta = integral(e^-x, l=0, u=0.5)

by sampling from Uniform(0, 0.5), and estimate the variance of ˆθ. Find
another Monte Carlo estimator θ∗ by sampling from the exponential
distribution. Which of the variances (of ˆθ and ˆθ∗) is smaller, and why?


```{r}
f = function(x) {
  return (exp(-x))
}
m = 1000
a = 0
b = 0.5
X = runif(m, a, b)

gx_hat = mean(f(X))
theta_hat = (b-a)*gx_hat
theta_hat
```
```{r}
estimate = replicate(m, expr = {
  X = runif(m, a, b)
  (b-a)*mean(-X)
})

mean(estimate)
var(estimate)
```


```{r}
theta_star = function(m) {
  X = rexp(m, 1)
  g = (f(-X) * (X>0) * (X<.5))/exp(-X)
  a = mean(g)
  b = var(g)
  
  return (c(a, b))
}

theta_star(m)
```      


6.4
```{r}
samples = 
```










