---
title: "BTTuan7"
output: html_document
date: "2023-03-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
(a) Generate a simulated data set as follows:
```{r}
set.seed(1)
x=rnorm(100)
y=x-2*x^2+rnorm(100)


```
In this data set, what is n and what is p? Write out the model
used to generate the data in equation form:

=> số quan sát (n): 100 , số biến (p): 2
=> model: y = x - 2*x^2 + e

(b) Create a scatterplot of X against Y . Comment on what you find.


```{r}
plot(x, y)
```

(c) Set a random seed, and then compute the LOOCV errors that
result from fitting the following four models using least squares:

```{r}

set.seed(192)
cv_errors = rep(0,4)
df = data.frame(x, y)
library(boot)
for (i in 1:4) {
  glmfit = glm(y~poly(x, i), data = df)
  cv_err = cv.glm(df, glmfit)$delta[1]
  cv_errors[i] = cv_err
  
  
}

cv_errors
```

(e) Which of the models in (c) had the smallest LOOCV error? Is
this what you expected? Explain your answer.
=> sai số của mô hình bậc 2 là nhỏ  nhất 

```{r}
glmfit = glm(y~poly(x,4), data=df)
summary(glmfit)
```





